Hydra Battles and Cie

### 2021-01-27 doc/chapter-powers.tex
remove an exercise

If we define $\varphi(a,b)  \left(
  \begin{array}{cc}
    a+b  & a \\
    a & b
  \end{array}
\right)$, then $\varphi(a,b)\times \varphi(c,d)=\varphi(ac + ad + bc, ac + bd)$, and
$\varphi(0,1)=  \left(
  \begin{array}{cc}
    1 & 0 \\
    0 & 1 
  \end{array}
\right) $.

@@

Since \texttt{computation} is an inductive family of types, 
it could be possible to define a composition operator that 
works like list appending (replacing the \texttt{Return y} of the first
computation with the second computation).
\emph{This approach is left as an exercise.}  The solution we present is based on functional programming and the concept of continuation.

\index{Exercises}
\begin{exercise}
Develop the approach suggested in the previous paragraph.  
\end{exercise}

>>>>

If we pose $\varphi(a,b) =\left(
  \begin{array}{cc}
    a+b  & a \\
    a & b
  \end{array}
\right)$, then $\varphi(a,b)\times \varphi(c,d)=\varphi(ac + ad + bc, ac + bd)$, and
$\varphi(0,1)=  \left(
  \begin{array}{cc}
    1 & 0 \\
    0 & 1 
  \end{array}
\right) $.

@@

  The solution we present is based on functional programming and the concept of continuation.
